% samknows and bismark
SamKnows\footnote{\url{http://www.samknows.com}} specializes in the deployment
of hardware-based probes that perform measurements to assess the performance
of broadband access networks. The probes function by performing active
measurements when the user is not aggressively using the network.  RIPE
Atlas\footnote{\url{https://atlas.ripe.net}} is another independent
measurement infrastructure deployed by the \ac{RIPE NCC}. It consists of
thousands of hardware probes distributed around the globe that perform
\ac{RTT} and traceroute measurements to a number of preconfigured destinations
alongside DNS queries to DNS root servers.

% measurement lab
\ac{M-Lab} \cite{dovrolis:2010} is an open, distributed platform to deploy
Internet measurement tools. The measurement results are stored on Google's
infrastructure. The tools vary from measuring TCP throughput and available
bandwidth to emulating clients to identify end-user traffic differentiation
policies \cite{dischinger:2010, kanuparthy:2011} to performing reverse
traceroute lookups from arbitrary destinations \cite{bassett:2010}.

% leone
It will only be possible to answer the aforementioned research questions with
access to a large-scale measurement platform. As partners of the Leone
consortium, we will leverage the infrastructure of our partners. We will
define metrics particularly targetted to our research questions and complement
them by implementing subsequent measurement tests. The developed measurement
tests will be deployed in our partner's networks, but may also become part of
SamKnows global infrastructure. The SamKnows infrastructure already has
several thousand deployed probes and will continue to grow during the
project's lifetime. The collected data will be conglomerated from multiple
measurement points and finally analyzed to uncover information needed to help
us answer these questions. This requires to develop data analysis algorithms
that can integrate data from different data sources such as address block
allocations from \ac{RIR}s or prefix and path information from BGP route
views. We have started with a study to assess how the user experience is
effected by the deployment of IPv6.
