The curiosity to understand the evolution of the Internet from the user'
vantage point started by establishing techniques to remotely probe the
broadband access network. Dischinger \emph{et al.} in \cite{dischinger:2007},
for instance, inject packet trains and use the responses received from
residential gateway to infer the broadband link characteristics. This led to
the development of a number of software-based solutions such as
\texttt{netalyzr} \cite{kreibich:2010}, that require explicit interactions
with the broadband consumer.  Recently, the requirement for accurate
measurements, coupled with \ac{FCC}' initiated efforts to define data-driven
standards, has led to the deployment of a number of large-scale measurement
platforms that perform measurements using dedicated hardware probes not only
from within the \ac{ISP}' network but also directly from the home gateway.

In a recent study, sponsered by the \ac{FCC}, Sundaresan \emph{et al.}
\cite{sundaresan:2011} have used such a measurement data from a swarm of
deployed SamKnows probes to investigate the throughput and latency of access
network links across multiple \ac{ISP}s in the United States. They have
coupled this data with their own Bismark platform \cite{sundaresan:2012} to
investigate different traffic shaping policies enforced by the \ac{ISP} and to
understand the bufferbloat phenomenon. The empirical findings of this study
has recently been repraised by Canadi \emph{et al.} in \cite{canadi:2012}
where they use crowdsourced data from \url{speedtest.net} to compare both
results. The primary aim of all these activities is to measure the performance
and reliability of broadband access networks and facilitate the regulators
with research findings to help them make policy decisions
\cite{draft-schulzrinne-lmap-requirements-00}.  As a result, the focus is on
defining metrics and implement measurement tests that help achieve this goal.

Using a large-scale measurement platform we want to take this further and
study the evolution of the Internet. We want to define metrics and implement
measurement tests that help us answer questions of the form:

\begin{itemize}
  \item \emph{How does the performance of IPv6 compare to that of IPv4 in the real world?}
  \item \emph{Can we identify a \ac{CGN} from a home gateway?}
  \item \emph{Can we identify multiple layers of NAT from a home gateway?}
  \item \emph{How much do web services centralize on \ac{CDN}s?}
  \item \emph{To what extend does the network experience depend on regionalization?}
\end{itemize}

In the past, we have performed an experimental evaluation of IPv6
transitioning technologies to identify how well current applications and
protocols interoperate with them \cite{vbajpai:2012}. We are now participating
in the Leone\footnote{\url{http://leone-project.eu}} project whose primary
goal is to define metrics and implement tests that can asses the end-user
quality of experience by analyzing data collected from several measurements
running on SamKnows probes.
